---
title: "work documentation"
author: "laetitia"
date: "10/21/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



*imported first table (table1) from excel
*cut out headers and footers by setting reading frame from A7:M492
```{r}
 library(readxl)
table1_pov_age_race <- read_excel("table1_pov_age_race.xlsx", 
     range = "A7:M492")
```


*renamed all columns
```{r}
colnames(table1_pov_age_race) <- c("Year",
"Total # of All People","# of All People, Below Poverty","% of All People, Below Poverty", 

"Total # of People Under 18", "# of People Under 18, Below Poverty","% of People Under 18, Below Poverty",

"Total # of People 18-64","# of People 18-64, Below Poverty","% of People 18-64, Below Poverty", 

"Total # of People Over 65", "# of People Over 65, Below Poverty","% of People Over 65, Below Poverty"
                                   )
```



*deleted rows 68, 93 (race was white and the 2 headings redundant)
*then created an observation subset for race being white from rows 68-130
```{r}
View(table1_pov_age_race)
table1_pov_age_race <- table1_pov_age_race[-c (68, 93), ]
dplyr:: slice(iris, 68:130)
```


*deleted all in-table header rows (race) (run this separately)
```{r}
table1_pov_age_race <- table1_pov_age_race[-c (131, 156,185,210,235,273,298,323,339,364,389,405,430), ]

```

*deleted excessive superscript numbers from the years and substituted those values in the column Year
```{r}
table1_pov_age_race$Year -> year
substring(year,1,4)

substring(year,1,4) ->table1_pov_age_race$Year
```

for next time: 
get rid of the NAs 
if i use excel: 
table1_pov_age_race <- read_xlsx("table1_pov_age_race.xlsx", na = "N")

code is na.strings= N and read.csv but rest is same for csv file. need to export "new" table into a csv file


