---
title: "OPM_SPM_time.rmd"
author: "laetitia"
date: "11/6/2024"
output: html_document
---

*libraries needed
```{r}
library(readxl)
library(shiny)
library(ggplot2)
library(lubridate)
library(plotly)

```



*imported table OPM and SPM from excel
*cut out headers and footers and limited data to total pop by setting reading frame from A2:F62
```{r}
OPM_SPM_table <- read_excel("OPM_SPM.xlsx", 
     range = "A2:F62")
```

*renamed columns for convenience and overview
```{r}
colnames(OPM_SPM_table) <- c("year", "Anchored SPM Rate without Taxes/Transfers", "Anchored SPM", "Historical SPM without Taxes/Transfers", "SPM_Poverty_Rate", "OPM_Poverty_Rate" )
                                   
```


*deleted excessive superscript numbers from the years and substituted those values in the column Year
```{r}
OPM_SPM_table$year -> year
substring(year,1,4)

substring(year,1,4) ->OPM_SPM_table$year
```

*deleted rows 48, 52, 55 (duplicates)
```{r}
OPM_SPM_table <- OPM_SPM_table[-c (2,4,7,48, 52,55,56), ]
```


*assigning values and organizing data
```{r}
OPM_SPM_table$SPM_Poverty_Rate -> SPM_Poverty_Rate
OPM_SPM_table$year -> year
OPM_SPM_table$Date <- make_date(year)
make_date(year) -> Year
```



*starting to graph SPM vs Year and making it interactive with plotly
```{r}
ggplotly(ggplot(data=OPM_SPM_table,aes (x = Year, y = SPM_Poverty_Rate)) + geom_point(color=4) + geom_line(color=4) + theme_classic() + labs(title="Graph of SPM Poverty Rate vs. Year",
        x ="Year", y = "SPM Poverty Rate"))
```



*starting to graph OPM vs year and making it interactive with plotly
```{r}
OPM_SPM_table$OPM_Poverty_Rate -> OPM_Poverty_Rate
ggplotly(ggplot(data=OPM_SPM_table, aes (x = Year, y = OPM_Poverty_Rate)) + geom_point(color=4) + geom_line(color=4) + theme_classic() + labs(title="Graph of OPM Poverty Rate vs. Year",
        x ="Year", y = "OPM Poverty Rate"))
```
