---
title: "pov_edu_work.rmd"
author: "laetitia"
date: "11/13/2024"
output: html_document
---
*libraries needed
```{r}
library(leaflet)
library(sf)
library(geojsonio)
library(htmltools)
library(htmlwidgets)
library(stringi)
library(RColorBrewer)
library(readr)
library(tidyverse)
library(dplyr)

```


*using CB's states shapefile, imported
```{r}
states <- read_sf('cb_2019_us_state_5m.shp')
```

*creating a map of the US, redefining each state with the SF
```{r}
m <- leaflet() %>%
  addProviderTiles(providers$CartoDB.PositronNoLabels)  %>% 
  setView(lng = -96.25, lat = 39.50, zoom = 4) %>% 
  addPolygons(data = states,
              weight = 1)
m
```

*imported poverty rates across state data csv file from census bureau
```{r}
CB_pov_overview <- read.csv("CB_pov_overview.csv", sep = ",")
```

*change column names of CB_pov_overview table
```{r}
colnames(CB_pov_overview) <- c("NAME", "FIPS", "Percentage", "Families Below Poverty", "Rank within US" )
```


*importing education dataset
```{r}
CB_edu_attain <- read_csv("CB_edu_attain.csv")
```

*cleaning education dataset, renaming needed columns
```{r}
CB_edu_attain <- CB_edu_attain[ -c(1:6,8:10)]
CB_edu_attain <- CB_edu_attain[-c (52:56), ]
colnames(CB_edu_attain) <- c("NAME","Pop_Density","Pop_Over_25")
colnames(CB_edu_attain)[27] = "Percentage_Bachelor"


```

*merging data with educational attainment
```{r}
CB_edu_attain$NAME -> NAME
CB_pov_overview$NAME -> NAME
states_geo_edu <-merge(states, CB_edu_attain, by='NAME', all.x = F)
```

*start coloring choropleth
```{r}
CB_edu_attain$Percentage_Bachelor -> Percentage_Bachelor
CB_edu_attain$Pop_Density -> Pop_Density
CB_edu_attain$Pop_Over_25 -> Pop_Over_25

paletteNum <- colorNumeric("Greens", domain = states_geo_edu$Percentage_Bachelor)

```


*adding coloring into leaflet code
```{r}

m <- leaflet(states) %>%
  addProviderTiles(providers$CartoDB.PositronNoLabels)  %>% 
  setView(lng = -96.25, lat = 39.50, zoom = 4) %>% addPolygons(data=states_geo_edu, color = 'white', weight = 1, smoothFactor = .3, fillOpacity = .75,fillColor = ~ paletteNum(Percentage_Bachelor))
m

```
*preparing text for interactive labels
```{r}
mytext1 <- paste(
  "State: ", states_geo_edu$NAME, "<br/>",
  "Population Aged 25 And Over: ", states_geo_edu$Pop_Over_25, "<br/>",
  "Population in Poverty (%): ", CB_pov_overview$Percentage, "<br/>",
  "Population Over 25 with a Bachelor's Degree (%): ", round(states_geo_edu$Percentage_Bachelor, 2), 
  sep = ""
) %>%
  lapply(htmltools::HTML)

```

*final map
```{r}
m <- leaflet(states) %>%
  addProviderTiles(providers$CartoDB.PositronNoLabels)  %>% 
  setView(lng = -96.25, lat = 39.50, zoom = 4) %>% addPolygons(data=states_geo_edu, color = 'white', weight = 1, smoothFactor = .3, fillOpacity = .75,fillColor = ~ paletteNum(Percentage_Bachelor), label = mytext1,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "13px",
      direction = "auto"
    )
  ) %>%
  addLegend(
    pal = paletteNum, values = ~Percentage_Bachelor, opacity = 0.9,
    title = "Bachelor's Degree Attainment and Poverty Statistics for Adults 25+", position = "bottomleft"
  )

m
```
