---
title: "work documentation"
author: "laetitia"
date: "10/21/2024"
output: html_document
---


*imported first table (table1) from excel
*cut out headers and footers by setting reading frame from A7:M492
```{r}
 library(readxl)
table1_pov_age_race <- read_excel("table1_pov_age_race.xlsx", 
     range = "A7:M492")
```


*renamed all columns
```{r}
colnames(table1_pov_age_race) <- c("Year",
"Total Number of All People","Number of All People Below Poverty","Percent of All People Below Poverty", 

"Total Number of People Under 18", "Number of People Under 18 Below Poverty","Percent of People Under 18 Below Poverty",

"Total Number of People 18-64","Number of People 18-64 Below Poverty","Percent of People 18-64 Below Poverty", 

"Total Number of People Over 65", "Number of People Over 65 Below Poverty","Percent of People Over 65 Below Poverty"
                                   )
```



*deleted rows 68, 93 (race was white and the 2 headings redundant)
```{r}
View(table1_pov_age_race)
table1_pov_age_race <- table1_pov_age_race[-c (68, 93), ]
```


*deleted all in-table header rows (race) (run this separately)
```{r}
table1_pov_age_race <- table1_pov_age_race[-c (131, 156,185,210,235,273,298,323,339,364,389,405,430), ]

```

*deleted excessive superscript numbers from the years and substituted those values in the column Year
```{r}
table1_pov_age_race$Year -> year
substring(year,1,4)

substring(year,1,4) ->table1_pov_age_race$Year
```

*exported table into a csv file
```{r}
write.csv(table1_pov_age_race, file= "table1.csv")
```

*then removed NA values (N in cells)
```{r}
table1_pov_age_race <- read.csv("table1.csv", na.strings = "N")
```

*then exported clean table1 into a new csv
```{r}
write.csv(table1_pov_age_race, file= "table1_clean.csv")
```

*creating value for column: Number of All People Below Poverty
```{r}
table1_pov_age_race$Number.of.All.People.Below.Poverty -> Number_People_Below_Pov
```

*then created an observation subset for race being white from rows 68-130
```{r}
dplyr:: slice(iris, 68:130)
```